State-of-the art monolithic electronic-silicon photonics processes are a monumental advancement in the co-design of electronic and photonics circuits.
For high speed application, sharing the same substrate has its advantages: no interconnection needed reducing the parasitic load, integrated simulation environment and simpler mechanical assembly of the integrated circuit (IC) into more complex systems.
Although, at the moment, even the best monolithic processes struggle to compete with recent CMOS nodes in terms of maximum frequency of operation for digital signal processing or the driving power needed for optical modulators. 
For lower speed application that do not need these higher speeds or driving power, monolithic nodes seems to be an enticing solution for its ease of use, embedded testing capabilities and easier physical assembly.
Nevertheless, since monolithic nodes are usually build upon an existing CMOS node and modified to fit the less strainuous fabrication of the photonics\CitationNeeded, they tend to exceed the price per area of similar CMOS processes\CitationNeeded. 

Integrating CMOS capabilities in a silicon photonics node, although possible, is relatively new. 
It creates a new avenue to access a monolithic node for researchers and industry without the high entry price.
Prior art has shown that integrating CMOS transistors into a conventionnal silicon photonics process is possible but limited\cite{zanetto_unconventional_2023,shekhar_roadmapping_2024}, as it shows poorer electrical performances than equivalent CMOS and has no foundry supplied electronic libraries.

In this paper, we aim to expand on the idea by proposing improvements on the transistor design, discussing the limitations and pitfalls of the implementation and tooling, and present the progress made towards a monolithic electronic platform in a conventional silicon photonics process.





%It forces the designers of integrated circuit systems to either choose multiple technologies, one dedicated for photonics and others for the CMOS DSP and slow control, and have the challenge of doing the co-design and interconnect or bend to monolithic . 
%As such, a system designer would want to use their monolithic area as best as they can, but they are confronted by three 
%The larger size of the silicon photonics circuits compared to their CMOS counterpart means that one pays the monolithic premium price 


%As the process is geared toward both CMOS and optical capabilities, the price of the area is superior to thoses of either the similar size CMOS or similar performance silicon photonics. 
%This creates a difficult choice for designers who wishes to make an integrated circuit system, either choose two technologies, one for the photonics and the other for the CMOS, and have the hassle of doing the co-design and interconnect or choosing the monolithic process and pay the increased price.
